Using Cell Phone Keyboards is \NP\ Hard

### 2010-05-31 slides/talk.tex
Changed the frac to a binom

\fst{Enumerating All Alphabetic Partitions}{
If we restrict ourselves to only the partitions which keep the letters in alphabetic order, then we can enumerate all $\frac{25!}{18!7!}$ partitions and test them over the course of a few days on a modern computer.

>>>>

\fst{Enumerating All Alphabetic Partitions}{
If we restrict ourselves to only the partitions which keep the letters in alphabetic order, then we can enumerate all $\binom{25}{7}$ partitions and test them over the course of a few days on a modern computer.
